Poincaré and SimBio: a versatile and extensible Python ecosystem for modeling systems.

### 2023-11-27 article.qmd
Add performance figure

To address these issues,
we developed poincaré and SimBio,
open-source Python packages for defining and simulating systems.
Poincaré allows to define differential equation systems
and SimBio builds on top of it to define reaction networks.
They are focused on providing an ergonomic experience for end-users
by integrating well with IDEs and static analysis tools
through the use of standard modern Python syntax.
They can be extended from Python
since they are coded in pure Python,
which is beneficial for power users.
TODO: high degree of flexibility,  large potential to leverage existing python tools.  For example, ....
Their models can be introspected to create other representations,
such as graphs connecting species and/or reactions,
or tables with parameters or equations.
Finally,
they have a modular architecture with a clear separation of concerns,
making it easier to maintain or to contribute new code,
which is beneficial for developers and maintainers.

@@

## Other things

units -> Pint
interactive

>>>>

To address these issues,
we developed poincaré and SimBio,
open-source Python packages for defining and simulating systems.
Poincaré allows to define differential equation systems
and SimBio builds on top of it to define reaction networks.
They are focused on providing an ergonomic experience for end-users
by integrating well with IDEs and static analysis tools
through the use of standard modern Python syntax.
They can be extended from Python
since they are coded in pure Python,
which is beneficial for power users.
For instance, it is easy to reuse integrators defined in other packages,
but it is also possible to change the compilation itself
(the )
Their models can be introspected to create other representations,
such as graphs connecting species and/or reactions,
or tables with parameters or equations.
Finally,
they have a modular architecture with a clear separation of concerns,
making it easier to maintain or to contribute new code,
which is beneficial for developers and maintainers.

@@

## Reproducibility and performance

![Performance of the different softwares to solve a subset of BioModels models. (left) Run time for model BIOMD3 as a function of the number of output points. (right) Run time for different models ordered according to the geometric mean of the run times.](src/performance/figures/performance.png){#fig-runtime}
